### 2024-10-20 src/Submission.Rnw
Things 2

>>>>

<<echo=TRUE>>=
head(ddat)

neg_log_likelihood <- function(params, data) {
  # Extract the parameters
  beta0 <- params[1]        # Intercept
  beta1 <- params[2]        # Slope
  sigma <- params[3]        # Standard Deviation

  # Extract dependent and independent variables
  x <- ddat$bmi
  y <- ddat$target

  # Predicted value of a linear model
  y_pred <- beta0 + beta1 * x

  # Log-likelihood for normal distribution
  norm_log_likelihood <- -sum(dnorm(y, mean = y_pred, sd = sigma, log = TRUE))

  return(norm_log_likelihood)
}
# Now to use optim() to minimise the negative log-likelihood and estimate params
int_params <- c(beta0 = 0, beta1 = 0, sigma = 1)

mle <- optim(
  par = int_params,           # Initial guess
  fn = neg_log_likelihood,    # The function being minimised
  data = ddat,            # Data to be used
  method = "BFGS",            # Optimisation method (less fragile and more common)
  hessian = TRUE              # Return Hessian for variance estimation
)

# Results
mle$par

# Predicted values from the model put back into likelihood function for LP
y_pred <- mle$par[1] + mle$par[2] * ddat$bmi

# Residuals
residuals <- ddat$target - y_pred

# Plot residuals to check for patterns
plot(ddat$bmi, residuals, main = "Residuals vs BMI", xlab = "BMI", ylab = "Residuals")
@
